---
title: "Finding the directions"
author: "Clara Schartner and Araya Eamrurksiri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package `ggdirections` includes a function `directions` that give you routes from the origin to the destination place.

## Purpose

This package will help the user find a route to their destination, and also give them the direction to go.

## Usage
The function can be used like this: `directions(origin, destination, avoid = NULL , travel_mode = "driving")`

## Function structure
`directions` function is consisted of two mains parameters and another two optional parameters.

1. `orgin` is the origin city 

1. `destination` is your destination city that you wish to go to

1. `avoid` indicates that the calculated route should avoid this typical features.

    * tolls
    * highways

1. `travel_mode` indicates the mode of travel

    * driving (default): the driving direction on the road
    * walking: the walking direction on the pedestrian.
    * bicycling: the bicycling direction on the bicycle path.

## How to use the function?

First, the most and important step of all is to load the `ggdirections` package into your R session.

```{r, echo=FALSE}
library(ggdirections)
```

Now, it's time to think about the place you have in mind and then put them on the `directions` function.

```{r}
directions("Barcelona", "Madrid")
```

The map appears the route from Barcelona to Madrid as you wish. The several red dots in the map indicate the intersection or crossing between the route.

### Avoid 
What if you want to avoid tolls or highways for your journey? You can put __bold__avoid parameter to the function. It will calculate new route avoiding such feature.

```{r}
directions("Barcelona", "Madrid", avoid = "tolls")
```

The map shows the route from Barcelona to Madrid. However, you can notice the slightly different between this map and the previous one ,and that is a movement of the red dots. The function is now calculated the new route for you which avoid the tolls. 

### Travel Mode
You can also put **bold**travel_mode parameter to the function as wll. The default for this parameter is set to "driving".

```{r}
directions("Barcelona", "Madrid", travel_mode = "walking")
```

The map, again, shows the route for you to go from Barcelona to Madrid by walking.


## References
