---
title: "Finding the directions"
author: "Clara Schartner and Araya Eamrurksiri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package `ggdirections` includes a function `directions` that give you routes from the origin to the destination place.
To be more specific it will provide the user with a map, where all intersections or turns between two places are marked by a red dot.

## Purpose

This package will help the user find a route to their destination by providing a map.

## Usage
The function can be used like this: `directions(origin, destination, avoid = NULL , travel_mode = "driving")`

## Function structure
`directions` function is consisted of two mandatory parameters and another two optional parameters.

1. `orgin` is the place where the journey starts

1. `destination` is your destination city which you wish to go to

1. `avoid` indicates that the calculated route should avoid one of these typical features.

    * tolls
    * highways
    * ferries

1. `travel_mode` indicates the mode of travel

    * driving (default): the driving direction on the road
    * walking: the walking direction on the pedestrian.
    * bicycling: the bicycling direction on the bicycle path.

## How to use the function?

First, the most and important step of all is to load the `ggdirections` package into your R session.

```{r, echo=FALSE}
library(ggdirections)
```

Now, it's time to think about the place you have in mind and then put them on the `directions` function.

```{r}
directions("Barcelona", "Madrid")
```

The map appears the route from Barcelona to Madrid. The several red dots in the map indicate the intersection or crossing on the route.

### Avoid 
What if you want to avoid tolls or highways for your journey? You can put __avoid__  parameter to the function. It will calculate new route avoiding such feature.

```{r}
directions("Barcelona", "Madrid", avoid = "tolls")
```

The map shows the route from Barcelona to Madrid. However, you can notice the difference between this map and the previous one because of the red dots. The function has now calculated the new route for you which avoid the tolls. 

### Travel Mode
You can also put __travel_mode__ parameter to the function as well. The default for this parameter is set to "driving".

```{r}
directions("Barcelona", "Madrid", travel_mode = "walking")
```

The map, again, shows the route for you to go from Barcelona to Madrid but this time walking.


## References
